Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-08-28 Paper/paper_draft.rmd
Update.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["myreferences.bib", "library.bib", "r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output:
  papaja::apa6_pdf:
    citation_package: biblatex
    includes:
        in_header: paper_draft_preamble.tex

@@

<!--
header-includes   :
  - \usepackage[utf8]{inputenc}
  - \usepackage[T1]{fontenc}
  - \usepackage{xcolor}
  - \usepackage{hhline}
  - \usepackage{mathtools}
  - \linespread{1}
  - \usepackage{gb4e}
  - \noautomath #trying to see why shorttitle does not appear in the other paper. when done like this it appears.
  - \usepackage{setspace}
  - \makeatletter
  - \apptocmd{\@exe}{\singlespacing}{}{}
  - \makeatother
  - \usepackage{sectsty}
  - \allsectionsfont{\large}
  - \usepackage{color}
  - \usepackage{hyperref}
  - \hypersetup{colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue} 
  - \usepackage[english]{babel}
  - \addto\extrasenglish{\renewcommand{\itemautorefname}{Item}}
  - \renewcommand*{\nameyeardelim}{\addcomma\space}
  - \usepackage{tikz}
  - \usepackage{tikz-qtree}
  - \let\eachwordone=\textit
  - \usepackage{geometry}
  - \geometry{margin=2cm}
  - \usepackage{libertine}
  - \usepackage{libertinust1math}
  - \usepackage[T1]{fontenc}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \rhead{Türk}
  - \lhead{Agreement Attraction in Turkish}
  - \rfoot{\thepage}
  - \usepackage{lmodern}

@@

<!--
    includes:
        in_header: paper_draft_preamble.tex
-->
<!--
Introduction:
 - Review of the key attraction findings: 
      * English. 
      * German: @ReifegersteEtAl:2016
      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
      * Arabic: @TuckerEtAl:2015
      * Spanish: @LagoEtAl:2015
      * Turkish: @LagoEtAl:2018
      * Hammerly 2018 [@HammerlyEtAl:2018]
      * @LinzenLeonard:2018
      * @SmithFranck:2018
      * @ParkerPhillips:2017
      * @VasishthEtAl:2017 **
      * @ReifegersteEtAl:2016
      * @KwonSturt:2016
      * @RisticMolinaroMancini:2016
      * @SlevcMartin:2016
      * @PatsonHusband:2015
      * @Enochson:2015 **
      * @FranckColonnaRizzi:2015
      * @WagersEtAl:2009
      * Slovak: @BadeckerKuminiak:2007
      * @BockEtAl:2001
      * @FiederEtAl:2014 **
      * @Staub:2009
      * @TannerNicolBrehm:2014
      * @XiangEtAl:2013
      * @NicenboimEtAl:2018

>>>>

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["myreferences.bib", "library.bib", "r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output:
  papaja::apa6_pdf:
    includes:
        in_header: paper_draft_preamble.tex

@@

<!--
    citation_package: biblatex

@@

<!--
Introduction:
 - Review of the key attraction findings: 
      * English. 
      * German: @ReifegersteEtAl:2016
      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
      * Arabic: @TuckerEtAl:2015
      * Spanish: @LagoEtAl:2015
      * Turkish: @LagoEtAl:2018
      * Hammerly 2018 [@HammerlyEtAl:2018]
      * @LinzenLeonard:2018
      * @SmithFranck:2018
      * @ParkerPhillips:2017
      * @VasishthEtAl:2017 **
      * @ReifegersteEtAl:2016
      * @KwonSturt:2016
      * @RisticMolinaroMancini:2016
      * @SlevcMartin:2016
      * @PatsonHusband:2015
      * @Enochson:2015 **
      * @FranckColonnaRizzi:2015
      * @WagersEtAl:2009
      * Slovak: @BadeckerKuminiak:2007
      * @BockEtAl:2001
      * @FiederEtAl:2014 **
      * @Staub:2009
      * @TannerNicolBrehm:2014
      * @XiangEtAl:2013
      * @NicenboimEtAl:2018
